### 2013-09-17 chi2014/introduction.tex
Minor edits to intro

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow logarithmic growth models, as a function of the total number of responses received, from all participants. In other words (and as one would expect), there are diminishing returns from asking more people to submit ideas. However, the actual rates differ per condition, as described below.
\item The rates for generating novel ideas are linked to the number of responses requested: The more responses requested from individuals, the higher the rate of novel idea generation, in general.
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. Our data suggest that the first 20 ideas are the most unoriginal (i.e., the most common). This finding complements the previous finding, and further suggests that there is little value in requesting fewer than 20 ideas from workers.
\item Individuals' patterns of idea generation mimic those identified by Nijstaf and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. In our data, we see the prevalence of riffing steadily increase over the first 20 responses, after which its prevalence plateaus.
\item Requesting ``as many ideas as possible'' for a fixed price is inadvisable, as it leads to a relatively low number of ideas produced (in our experiments, fewer than 20)
\end{itemize}

>>>>

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow logarithmic growth models, as a function of the total number of responses received, from all participants. In other words (and as one would expect), there are diminishing returns from asking more people to submit ideas. However, the actual rates differ per condition, as described below.
\item The rates for generating novel ideas are linked to the number of responses requested: The more responses requested from individuals, the higher the rate of novel idea generation, in general.
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. Our data suggest that the first 20 ideas are the most unoriginal (i.e., the most common). This finding complements the previous finding, and further suggests that there is little value in requesting fewer than 20 ideas from workers.
\item Individuals' patterns of idea generation mimic those identified by Nijstaf and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. In our data, we see the prevalence of riffing steadily increase over the first 20 responses, after which its prevalence plateaus.
\item Requesting ``as many ideas as possible'' for a fixed price (fixed for the entire HIT, rather than per idea) is inadvisable, as it leads to a relatively low number of ideas produced (in our experiments, fewer than 20)
\end{itemize}
